---
title: "Statistical Inference Project"
author: "AVA"
date: "Thursday, January 22, 2015"
output: html_document
---
# Part A
## Overview

In this project, we have investigated the exponential distribution in R and then,  we have compared it with the Central Limit Theorem. The exponential distribution can be simulated in R with << rexp(n, lambda) >> where lambda is the rate parameter.

The mean of the exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Lambda parameter was set to 0.2 for all simulations. We have investigated the distribution of averages of 40 exponentials.

We embeded the following R code chunks :

## Simulations

### The distribution of averages

1. We have considered the distribution of a large collection of averages of 40 exponentials (the distribution of 1000 averages of 40 random exponentials). 

```{r}
lambda <-  0.2
n <- 40
nosim <- 1000
set.seed(1)
collectiondata <- rexp(nosim * n, lambda)
matrixdata <- matrix(collectiondata, nrow=nosim, ncol=n)
str(matrixdata)
means <-  apply(matrixdata, 1, mean)
str(means)
# 1. Show the sample mean and compare it to the theoretical mean of the distribution.
mean(means)
1/lambda
# 2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution
var(means)
sd(means)
(1/lambda)/sqrt(n)
# 3. Show that the distribution is approximately normal.
hist(means)
```



### The exponential distribution

2. Then we compared it with the distribution of a large collection of random
exponentials (the distribution of 1000 random exponentials).

```{r, echo=TRUE}
lambda <-  0.2
n <- 40
set.seed(1)
expdistribution <- rexp(1000, lambda)
str(expdistribution)
mean(expdistribution)
var(expdistribution)
sd(expdistribution)
1/lambda
(1/lambda)/sqrt(n)
hist(expdistribution)
```

Note that the mean of the distribution of 1000 averages of 40 random exponentials(0.2) is 4.99, which is very close to the expected mean (1/lambda = 5.0).
